Optimal (Multiway) Spatial Joins

### 2024-05-22 msj.tex
yufei

Our subsequent discussion will proceed as follows. In Section~\ref{sec:hv:type1}, we

>>>>

Our subsequent discussion will proceed as follows.  Section~\ref{sec:hv:type1} will explain how to produce all the result tuples of Type 1. Section~\ref{sec:hv:type2} will explain how to produce the result tuples $(r_1, ..., r_{k-2}, h, v)$ of a particular sub-type of Type 2: those tuples where $r_1$ covers the left endpoint of $h$. Other sub-types can be computed using the same algorithm, by symmetry.

A remark is in order about duplicate removal. A result tuple of Type 2 can belong to, in the worst case, all the $4(k-2)$ sub-types. Hence, by considering each sub-type separately, we may see the same result tuple multiple times (precisely, up to $4(k-2)$ times) in the whole algorithm. However, this does {\em not} mean that the tuple need to be {\em reported} multiple times. Whenever a Type-2 result tuple is found, we can immediately decide all the sub-types it belongs to. To avoid outputting the tuple more than once, it suffices to
